Block bootstrap consistency\\under weak assumptions

### 2015-12-31 subs/ETr2/reply_3.tex

\begin{document}
\section*{\hfill Reply to referee 3\hfill}

@@

>>>>

\begin{document}
\section*{\hfill Reply to referee 3\hfill}
\section*{General summary of changes}
This version of the paper has the following changes from the
previous submission:
\input{summary}

\section*{Reply to specific points}

@@

  I have added a formal specification of the top-level probability
  space at the beginning of the mathematical appendix. You are
  right, this has made it easier to make precise statements in some
  of the results\,---\,e.g. the statement of Lemma~2 and the proof
  of Lemma~5. Thank you for this suggestion.  I will also point out
  that the paper defines several important sub-sigma-fields as they
  are necessary for the proofs, which gives additional clarity and
  formalism, and I have tried to improve in this respect in this
  version of the paper.
